### 2018-07-20 fe_px_paper/fe_body_text.tex
Finished 1st draft of results and conclusions sections.

The work described herein follows the  methods utilized in our recent work and established by Graves \etal\ 
% for the measurement of cross sections in stacked target irradiations   
for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018a,Graves2016}.
Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.

\comment{Do we really need to cite Alex's thesis?}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth]{./figures/SAM_2494.JPG}
 % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
 \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack, before it was mounted in the beamline. The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor is visible at the front of the stack.}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:before_minimization}
   \hspace{-5pt}}%
     \subfloat{
        \centering

@@

>>>>

The work described herein follows the  methods utilized in our recent work and established by Graves \etal\ 
% for the measurement of cross sections in stacked target irradiations   
for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018a,Graves2016}.
% 
% Make sure to add this back in for the journal article
% 
% 
% Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.

% \comment{Do we really need to cite Alex's thesis?}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth]{./figures/SAM_2494.JPG}
 % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
 \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack, before it was mounted in the beamline. The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{../nb_px_paper/figures/before_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:before_minimization}
   \hspace{-5pt}}%
     \subfloat{
        \centering

@@

\subsection{Measurement of nuclear excitation functions}

After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
With the exception of two foils (Cu-20 and Ti-20), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provided the first evidence (before gamma-ray spectrometry) that the beam was stopped in the stack between Fe-14 and Ti-20.
Using the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of \textred{198.8$\pm$6.7\,nAh} was calculated to be incident upon the 55\,MeV target stack using the MCNP6 fluence model, and a  fluence of \textred{196.9$\pm$11.3\,nAh} using the linear fit model.
Similarly, for the 25\,MeV stack, a fluence of \textred{198.8$\pm$6.7\,nAh} was calculated to be incident upon the 55\,MeV target stack using the MCNP6 fluence model, and a  fluence of \textred{196.9$\pm$11.3\,nAh} using the linear fit model.
\textred{All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the beamline current integrators.}
\textred{As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.}
This incident fluence dropped by approximately \textred{8.9\% to  180.9$\pm$5.4\,nAh (and by 7.2\% to  182.7$\pm$13.5\,nAh using the linear fit model)} over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Voyles2018a,Graves2016}.
This loss of fluence is due to a combination of 
% beam utilization for the various 
(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

Using the final proton fluence at each energy position, cross sections for  \textred{(list of residual products)} were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils in the \textred{0--55\,MeV} region, as recorded in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu} foils, the (p,x) cross sections for  \textred{(list of residual products)} were extracted, as recorded in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti} foils, the (p,x) cross sections for  \textred{(list of residual products)} were extracted, as recorded in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \textred{\ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb}} were  extracted and are recorded in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity \textred{($\pm$3--7\%), proton fluence ($\pm$4--6\%), and foil areal density ($\pm$0.1--0.6\%).}
% \comment{Update these with new numbers!\\ Stephen: Very impressive, if you feel this is realistic. }

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Fe}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:fe_rp_table}
\small
% \resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
% \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
% \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
% \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
% \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
% \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
% \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
% \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
% \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
% \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
% \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
\end{tabular}
% }
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:cufe_rp_table}
\small
% \resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
% \ce{^{51}Cr}\,($\sigma_c$)  & $0.919\pm0.079$         & $0.373\pm0.023$         & $0.450\pm0.028$         & $0.303\pm0.016$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{52}Mn}\,($\sigma_c$)  & $1.70\pm0.11$           & $0.570\pm0.031$         & $0.0407\pm0.0022$       & $0.00526\pm0.00057$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{52g}Mn}\,($\sigma_i$) & $0.673\pm0.043$         & $0.239\pm0.018$         & $0.0164\pm0.0023$       & $0.000986\pm0.000053$   & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{52m}Mn}\,($\sigma_c$) & $1.023\pm0.091$         & $0.331\pm0.030$         & $0.0244\pm0.0036$       & $0.00427\pm0.00052$     & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{54}Mn}\,($\sigma_i$)  & $5.87\pm0.37$           & $3.77\pm0.21$           & $4.14\pm0.22$           & $4.84\pm0.26$           & $1.680\pm0.091$         & --\cmmnt{\hrulefill}    \\
% \ce{^{55}Co}\,($\sigma_c$)  & $1.71\pm0.11$           & $1.015\pm0.058$         & $0.193\pm0.012$         & $0.0299\pm0.0028$       & $0.00235\pm0.00022$     & --\cmmnt{\hrulefill}    \\
% \ce{^{56}Ni}\,($\sigma_c$)  & $0.0806\pm0.0051$       & $0.1005\pm0.0055$       & $0.0906\pm0.0046$       & $0.0304\pm0.0016$       & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{57}Ni}\,($\sigma_c$)  & $1.465\pm0.093$         & $1.202\pm0.065$         & $1.400\pm0.071$         & $2.13\pm0.11$           & $1.565\pm0.083$         & $0.0262\pm0.0015$       \\
% \ce{^{57}Co}\,($\sigma_i$)  & $40.1\pm2.5$          & $35.6\pm1.9$          & $35.8\pm1.8$          & $48.5\pm2.5$            & $47.7\pm2.5$            & $3.21\pm0.18$           \\
% \ce{^{58}Co}\,($\sigma_c$)  & $57.7\pm4.5$            & $55.0\pm4.7$            & $42.7\pm3.4$            & $33.7\pm2.8$            & $39.0\pm3.8$            & $62.3\pm4.6$            \\
% \ce{^{58g}Co}\,($\sigma_i$) & $14.0\pm2.5$            & $10.8\pm2.1$            & $6.1\pm1.6$             & $7.8\pm1.4$             & $7.1\pm1.7$             & $1.12\pm0.32$           \\
% \ce{^{58m}Co}\,($\sigma_i$) & $43.6\pm3.7$            & $44.2\pm4.3$            & $36.6\pm3.0$            & $25.8\pm2.5$            & $31.9\pm3.3$            & $61.1\pm4.6$            \\
% \ce{^{59}Fe}\,($\sigma_c$)  & $0.865\pm0.057$         & $0.837\pm0.046$         & $0.749\pm0.039$         & $0.616\pm0.034$         & $0.209\pm0.014$         & --\cmmnt{\hrulefill}    \\
% \ce{^{60}Co}\,($\sigma_c$)  & $13.23\pm0.87$          & $13.47\pm0.78$          & $11.14\pm0.94$          & $11.44\pm0.80$          & $9.30\pm0.87$           & $6.6\pm1.1$             \\
% \ce{^{61}Cu}\,($\sigma_c$)  & $50.5\pm3.3$            & $56.1\pm3.2$            & $65.1\pm3.6$            & $72.2\pm4.0$            & $80.6\pm4.7$            & $157.1\pm8.6$           \\
\ce{^{64}Cu}\,($\sigma_i$)  & $38.7\pm2.7$            & $42.8\pm2.4$            & $45.5\pm2.7$            & $50.2\pm2.8$            & $55.7\pm3.0$            & $63.3\pm3.6$                 \\ \bottomrule
\end{tabular}
% }
\end{table}
\caption{Measured cross sections for the various \ce{^{nat}Ti}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:ti_rp_table}
% Disable next line for journal submission
% \resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
% \ce{^{82m}Rb}\,($\sigma_c$) & $2.48\pm0.22$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{83}Sr}\,($\sigma_c$)  & $4.02\pm0.61$           & $4.78\pm0.42$           & $3.49\pm0.36$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{85}Y}\,($\sigma_c$)   & $13.78\pm0.55$          & $7.52\pm0.51$           & $2.11\pm0.14$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{85g}Y}\,($\sigma_i$)  & $2.37\pm0.11$           & $2.08\pm0.17$           & $0.557\pm0.037$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{85m}Y}\,($\sigma_i$)  & $11.41\pm0.54$          & $5.44\pm0.48$           & $1.55\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{86}Zr}\,($\sigma_c$)  & $12.68\pm0.68$          & $18.21\pm0.93$          & $19.28\pm0.97$          & $6.16\pm0.32$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{86}Y}\,($\sigma_i$)   & $33.4\pm1.8$            & $41.6\pm2.2$            & $39.9\pm2.1$            & $13.56\pm0.72$          & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{87}Zr}\,($\sigma_c$)  & $47.4\pm7.3$            & $28.0\pm2.8$            & $32.2\pm2.9$            & $49.8\pm5.0$            & $38.2\pm3.7$            & $1.12\pm0.17$           \\
% \ce{^{87}Y}\,($\sigma_i$)   & $110.0\pm7.2$           & $54.7\pm2.8$            & $61.0\pm2.9$            & $90.0\pm4.9$            & $67.2\pm3.6$            & $2.91\pm0.17$           \\
% \ce{^{87g}Y}\,($\sigma_i$)  & $28.0\pm5.8$            & $7.4\pm1.3$             & $6.55\pm0.64$           & $5.8\pm2.2$             & $2.63\pm0.47$           & $0.942\pm0.073$         \\
% \ce{^{87m}Y}\,($\sigma_i$)  & $82.0\pm4.3$            & $47.3\pm2.5$            & $54.4\pm2.8$            & $84.2\pm4.4$            & $64.6\pm3.6$            & $1.97\pm0.15$           \\
% \ce{^{88}Zr}\,($\sigma_c$)  & $159.1\pm7.8$           & $144.6\pm6.8$           & $62.4\pm3.1$            & $21.2\pm1.0$            & $33.6\pm1.8$            & $65.3\pm4.0$            \\
% \ce{^{88}Y}\,($\sigma_i$)   & $17.2\pm1.1$            & $13.27\pm0.86$          & $7.98\pm0.72$           & $2.91\pm0.25$           & $9.2\pm1.4$             & $9.88\pm0.69$           \\
% \ce{^{89}Nb}\,($\sigma_c$)  & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $179\pm14$              & $214.4\pm9.8$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{89g}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $145\pm14$              & $186.4\pm9.6$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{89m}Nb}\,($\sigma_i$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $34.7\pm2.6$            & $28.0\pm2.0$            & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
% \ce{^{89}Zr}\,($\sigma_i$)  & $211\pm11$              & $243\pm13$              & $294\pm15$              & $257\pm13$              & $55.4\pm3.0$            & $15.5\pm1.0$            \\
% \ce{^{90}Mo}\,($\sigma_i$)  & $21.3\pm1.1$            & $26.4\pm1.3$            & $34.5\pm1.6$            & $61.9\pm3.1$            & $122.0\pm6.1$           & $24.2\pm1.5$            \\
% \ce{^{90}Nb}\,($\sigma_i$)  & $158.3\pm8.1$           & $174.9\pm8.5$           & $209.3\pm9.9$           & $272\pm14$              & $369\pm19$              & $163.9\pm9.8$           \\
% \ce{^{91m}Nb}\,($\sigma_c$) & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $66.5\pm5.8$            \\
% \ce{^{92m}Nb}\,($\sigma_i$) & $43.7\pm2.4$            & $47.3\pm2.4$            & $49.8\pm2.6$            & $52.9\pm2.8$            & $55.3\pm3.1$            & $59.9\pm3.9$            \\
\ce{^{93m}Mo}\,($\sigma_i$) & $0.97\pm0.20$           & $1.29\pm0.15$           & $1.62\pm0.24$           & $1.85\pm0.15$           & $1.86\pm0.14$           & $2.00\pm0.15$               \\ \bottomrule
% }

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured isomer-to-ground-state branching ratios for the various \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and \ce{^{nat}Ti}(p,x) reaction products observed in this work.}
\label{tab:fe_ibr_table}
\small
% \resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
                               & \multicolumn{6}{c}{Isomer branching ratio}                                                                                                                \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)             & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
\ce{^{nat}Cu}(p,x)\ce{^{52}Mn} & $0.603\pm0.066$         & $0.581\pm0.062$         & $0.598\pm0.095$         & $0.81\pm0.13$           & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
\ce{^{nat}Cu}(p,x)\ce{^{58}Co} & $0.757\pm0.088$         & $0.80\pm0.10$         & $0.858\pm0.099$         & $0.767\pm0.097$         & $0.82\pm0.12$           & $0.98\pm0.10$            \vspace{1em}     \\ 
E$_\text{p}$ (MeV)             & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
\ce{^{nat}Nb}(p,x)\ce{^{85}Y}  & $0.828\pm0.051$         & $0.724\pm0.080$         & $0.736\pm0.080$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\
\ce{^{nat}Nb}(p,x)\ce{^{87}Y}  & $0.746\pm0.063$         & $0.865\pm0.063$         & $0.893\pm0.063$         & $0.936\pm0.070$         & $0.961\pm0.075$         & $0.676\pm0.065$         \\
\ce{^{nat}Nb}(p,x)\ce{^{89}Nb} & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    & $0.193\pm0.021$         & $0.130\pm0.011$         & --\cmmnt{\hrulefill}    & --\cmmnt{\hrulefill}    \\ \bottomrule
\end{tabular}
% }
\end{table}

\textred{Placeholder text follows...fill in actual discussion of results...}

These results have several notable features.
The various \ce{^{nat}Cu}(p,x) cross sections measured here are in excellent agreement with the body of measurements in the literature,  but have been measured nearly exclusively with the highest precision to date.
Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the reactions presented here.
Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.

% Furthermore, t
This work presents the first measurements of several observables in 
% these mass regions.
% This work reports the first experimental measurement of
this mass region, including the \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction in the 40--90\,MeV region, 
% It also represents  the first measurement of 
the independent cross section for       \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratio via \ce{^{nat}Cu}(p,x).  
The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Cu}(p,x)\ce{^{52}Mn} cross section.
Similarly, this work offers the first measurement of the independent cross sections for \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y},  as well as the first measurement of the     \ce{^{85\text{m}}Y} (\nicefrac{9}{2}$^+$) / \ce{^{85\text{g}}Y}   (\nicefrac{1}{2}$^-$)
% (${^{1}/_{2}}^{-}$)
% ($\sfrac{1}{2}^-$) 
isomer branching ratio via \ce{^{nat}Nb}(p,x).

\textted{Comment on details of 51/52Mn production here...}

Notably, this work is the most well-characterized measurement of the \ce{^{nat}Nb}(p,x)\ce{^{90}Mo} reaction below 100\,MeV to date, with cross sections measured  at the 4--6\% uncertainty level.
This is important, as it presents the first step towards characterizing this reaction for use as a proton monitor reaction standard below 100\,MeV.
% The quantification of \ce{^{90}Mo} activity proved to be one of the most straightforward of all reaction products observed in this work.
\ce{^{nat}Nb}(p,x)\ce{^{90}Mo} can only be populated through the (p,4n) reaction channel, so no corrections for (n,x) contamination channels or decay down the A=90 isobar are needed.
% , which makes activity quantification trivial.
% In addition, 
\ce{^{90}Mo}  possesses seven strong, distinct gamma lines which can easily  be used for its identification and quantification.
Finally, the production of \ce{^{90}Mo}  in the 40--90\,MeV region is quite strong, with a peak cross section of approximately 120 mb.
Combining the reaction yield and gamma abundance, the use of approximately 23\,mg/cm$^2$ Nb targets easily provided sufficient counting statistics for activity quantification in the 40--90\,MeV region.
This result presents the first step towards the use of \ce{^{90}Mo} as a clean and precise   charged particle monitor reaction standard in irradiations up to approximately 24\,h in duration.

\textred{Placeholder text follows...Comment on production pathways of medical radionuclides...}

In addition to the $^\text{nat}$Nb(p,x)\ce{^{90}Mo} measurement, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
These include the non-standard positron emitters 
\ce{^{57}Ni} \cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
\ce{^{64}Cu} \cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},  \ce{^{86}Y} \cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
\ce{^{89}Zr}  \cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
\ce{^{90}Nb} \cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the Auger-therapy agent \ce{^{82\text{m}}Rb} \cite{Kovacs1991,Titarenko2011}. 
Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Cu}(p,x) and  \ce{^{nat}Nb}(p,x). 
The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co} \cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination \cite{MICHEL1997153,Ditrói2013}.

\subsection{Comparison of reaction modeling with experimental results}

% In this work
As mentioned before, cumulative cross sections are reported here for the first observable product nuclei in a mass chain, or whenever it is impossible to use decay spectrometry to distinguish direct production of a nucleus from decay feeding.
For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections are reported, allowing for determination of the direct production via subtraction.  
This, in turn, offers the opportunity to 
% use these data to gain insight into 
gauge the predictive capabilities of modern nuclear models used in the reaction evaluation process.  
The reaction channels with independent cross sections were compared to calculations with the reaction modeling codes EMPIRE, TALYS, and CoH, run with the default settings. 
The default optical models and E1 gamma strength function models for each code are presented in Table \ref{tab:defaults}. 
The large energy range covered by many of the exit channels, which extends significantly beyond the range of pure compound nuclear/evaporation, allows the data to be used to study the differences between these modeling codes in the  pre-equilibrium regime.
% All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.

The default level density in both CoH and TALYS is the Gilbert-Cameron model, which uses a Constant Temperature model below a critical energy and Fermi Gas model above it.
% \cite{add_level_density_models_here}. 
The default level density in EMPIRE is the Enhanced Generalized Superfluid Model (EGSM) which uses the Generalized Superfluid model below a critical energy, and Fermi Gas model above it \cite{Capote2009}.
% \cite{add_level_density_models_here}.
The EGSM densities are normalized to $D_0$ and the discrete levels, but in such a way that only the level density below the neutron separation energy is  effected by the discrete levels chosen for the normalization.  
All three codes use a two-exciton phenomenological model to calculate the pre-equilibrium cross section, but the specific implementation differs between the codes.

% \def\arraystretch{1.5}
\begin{table}
 \caption{Default settings for the reactions codes}
 \label{tab:defaults}
 \resizebox{\textwidth}{!}{%
\begin{tabular}{ c c c c}

 \underline{Code Version} & \underline{Proton/Neutron Optical Model} & \underline{Alpha Optical Model}  & \underline{E1 $\gamma$SF Model}  \\ 
 EMPIRE-3.2.3\cite{Herman2007}       & Koning-Delaroche\cite{Koning2003} & Avrigeanu(2009)\cite{Avrigeanu2009}       & Modified Lorentzian\cite{belgya2006handbook}  \\  
 TALYS-1.8\cite{Koning2012}          & Koning-Delaroche & Specific folded potential\cite{Koning2012}      & Brink-Axel Lorentzian\cite{Koning2012}   \\
  CoH-3.5.1\cite{kawano2003coh,KAWANO2010} & Koning-Delaroche     & Avrigeanu(1994)\cite{Avrigeanu1994} & Generalized Lorentzian\cite{kawano2003coh,KAWANO2010}

\end{tabular}
}
\end{table}
